Model Checking Differentially Private Properties

### 2018-01-26 applications.tex
reorganize presentation

In stream
processing mechanisms, input data are retrieved and analyzed
continuously.

Continual observation is commonly found in on-line service
providers~\cite{DNPR:10:DPCO,DNPRY:10:PPSA}. 
Consider monitoring events $a$ and $b$ by streaming inputs. We would
like to compute the number of event types occurred in inputs.

>>>>

Streaming processing gives another motivating example for Markov
decision processes. In stream processing, input data are retrieved and
analyzed continuously. Such continual observation is commonly found
in social media, service providers, or even electronic surveillance
systems. To protect privacy, privacy-respecting mechanisms must be
formulated and designed. Classical differential privacy however is
insufficient in streaming processing. Note that observations are of
indefinite lengths in such applications. All differentially private
mechanism necessarily stay in their internal states indefinitely
before outcomes are produced. Although differential privacy demands
privacy-respecting outcomes, internal states may reveal private
information in such mechanisms. When differentially private mechanisms
are in their internal states, privacy is still lost if an intrusion
occurs.

In pan privacy, data analysis mechanisms are required to respect
privacy even in their internal states~\cite{DNPR:10:DPCO,DNPRY:10:PPSA}. 
The idea is to show reachability probabilities are similar on
neighboring observations. In the following, we model a discrete
variant of the mechanisms by Markov decision processes. We will also
specify pan privacy on our model using $\dpCTL$.

Consider monitoring events of the types $a$ and $b$ continuously. An
observation is a sequence of event types. Two obsevations are
{neighbors} if one can be obtained from the other by replacing 
event types any number of times, that is, if they are of the same
length. \bw{Later, we will consider a different definition of
neighborhood by restricting the number of replacements.} 
We would like to compute the number of event types in
observations. Hence for observations $a \cdots a$ and $b \cdots b$ of
arbitrary positive lengths, the query result is $1$; and the query
result is $2$ for other non-empty observations.
